---
title: "Daily Briefing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("daily-brief")
```

## `r format(Sys.time(),'%a %b %d %Y')`

Welcome to your daily briefing. Today the high temperature will be `r round(weather$main$temp,digits=0)` degrees and `r weather$weather$main`.

```{r echo=FALSE, results='asis'}
library(knitr)
kable(events[c(1,2,3,5)], caption="Your Schedule")
```

In world news, the top 5 headlines and their sources are:
```{r echo=FALSE, results='asis'}
cat(paste(
  '<ul><li><a href=',
  news.df$articles$url[1],'>',
  news.df$articles$title[1],'</a></li><li><a href=',
  news.df$articles$url[2],'>',
  news.df$articles$title[2],'</a></li><li><a href=',
    news.df$articles$url[3],'>',
  news.df$articles$title[3],'</a></li><li><a href=',
    news.df$articles$url[4],'>',
  news.df$articles$title[4],'</a></li><li><a href=',
  news.df$articles$url[5],'>',
  news.df$articles$title[5],'</a></li></ul>'))

```

Here are your stock quotes from the last trading day:
```{r echo=FALSE, results='asis'}
stocks <- rbind(dji,aapl,goog)
kable(stocks)
```



Finally, to wrap up your briefing, today's inspirational quote:

>`r quote.df$contents$quotes$quote` -*`r quote.df$contents$quotes$author`*

